Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-20 draft.tex

@@

@@

@@

At some point along the evolutionary pathway, galaxies begin to cease star formation due to a combination of processes that together are known as quenching. In our model of mass assembly the characteristic mass at which quenching occurs is described by Eq. \ref{eq:mq}, and the rate of the transition from star forming to passive (as a function of the stellar mass) is determined by the transition scale $sigma_{\mathrm{Q}}$ which we set to 1.1 based on GAMA observations. It is possible that this transition is too narrow and that quenching happens too fast in our model, leading to an under-prediction of the prompt fraction of SNe in the highest mass galaxies. To address this issue we rerun the mass assembly model with $sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.

@@

>>>>

\subsection{Rate per unit stellar mass \label{subsec:snum}}
\textbf{short section showing SNUM and how it matches past results}

@@

\textbf{Add plot showing that the toy model recreates the stellar mass function?}

@@

\textbf{Or's suggestion: Fix beta, A and fit for tp}

@@

At some point along the evolutionary pathway, galaxies begin to cease star formation due to a combination of processes that together are known as quenching. In our model of mass assembly the characteristic mass at which quenching occurs is described by Eq. \ref{eq:mq}, and the rate of the transition from star forming to passive (as a function of the stellar mass) is determined by the transition scale $\sigma_{\mathrm{Q}}$ which we set to 1.1 based on GAMA observations. It is possible that this transition is too narrow and that quenching happens too fast in our model, leading to an under-prediction of the prompt fraction of SNe in the highest mass galaxies. To address this issue we rerun the mass assembly model with $\sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.

@@

\section*{Software}

All software used in this publication is publicly available. In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{Price-Whelan2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn}, and \texttt{arviz} \citep{Kumar2019}.
